eRNA and mRNA

### 2018-11-26 S6_eRNA/plot_eRNA.Rmd
remove big files

---
title: "eRNA and mRNA"
author: "Andrew Holding"
date: "1/31/2018"
output:
  html_document: default
  pdf_document: default
---

@@

## Effect of GRHL2 overexpression on mRNA transcription

```{r mRNA, fig.cap="Effect of GRHL2 expression on E2 responsive genes."}
qpcr<-read.csv("txt/QPCR GREB1 XBP1 TFF1.csv", header=TRUE)
df<-data.frame(qpcr)

p <- ggboxplot(df, x = "Sample", y = "Expression", ylab="Relative Expression",
               xlab="Condition",
               color = "Sample", palette =c("#00AFBB", "#E7B800", "#FC4E07"),
               add = "jitter", shape = "Sample", facet.by="Target",
               outlier=FALSE)

my_comparisons <- list( c("Ctrl", "siGRHL2"), c("Ctrl","GRHL2-DDK"))
p + 
    stat_compare_means(comparisons = my_comparisons,method="t.test", paired=TRUE)  +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

>>>>

---
title: "eRNA and mRNA"
author: "Andrew Holding"
date: "1/31/2018"
output:
  pdf_document: default
---

@@

## Effect of GRHL2  and GRLH2 delta 425-437 overexpression on eRNA transcription

```{r delta, fig.cap="Overexpression of GRHL2 delta 425-437."}
eRNA<-read.csv("txt/oe.csv")

eRNA<-eRNA[1:135,]

p <- ggboxplot(eRNA, x = "Condition", y = "Fold",
                   add = "jitter", color="Condition",
                   facet.by=c("Gene","CellTye"),ylab="Relative eRNA levels to empty vector")
comp.ev<-list(c("delta","OE"),c("delta","EV"),c("EV","OE"))
p2<-p + stat_compare_means(comparisons=comp.ev,
                           method = "t.test",paired=TRUE,alternative="greater",label.y=c(1.25,1.35,1.45))
p2
